### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:18	11:24:19	(Tue18.Mar)

\ans{It is clear we had to state this better upfront. In the 5th paragraph of the introduction we now explain that our system is a well sampled wideband sonar.}

@@

\ai{Thank you. We mention in the beginning of section IIA that we pre-steer to every angle and range bin in the image. but will try to express this with greater clarity and emphasize that we are operating in the near field.}

@@

\qi{Authors show solution of MVDR optimization as $\w = \frac{\Ri\1}{\1\T\Ri\1}$ and state this is the broadside solution. Are the authors pre-steering the array for every angle? Or are they using $w = \frac{\Ri\s}{\s\t\Ri\s}$ at off-broadside angles, with $\s$ the conventional steering vector (which would be a frequency-domain phase-shift vector, to be applied to a narrowband signal)? Pre-steering would enable disparate frequencies over a wide band to be coherently summed, to provide coherent gain in the look direction (over the band) by providing additional sample support for the sample covariance estimation.}

>>>>

\ans{Thank you, it seems we should state this better upfront. In the 5th paragraph of the introduction we now explain that our system is a well sampled wideband sonar.}

@@

\ai{Thank you. We mention in the beginning of section IIA that we pre-steer to every angle and range bin in the image, but now repeat this in IIA paragraph 3, and state that we operate in wideband conditions in the introduction.}

@@

\qi{Authors show solution of MVDR optimization as $\w = \frac{\Ri\1}{\1\T\Ri\1}$ and state this is the broadside solution. Are the authors pre-steering the array for every angle? Or are they using $\w = \frac{\Ri\s}{\s\t\Ri\s}$ at off-broadside angles, with $\s$ the conventional steering vector (which would be a frequency-domain phase-shift vector, to be applied to a narrowband signal)? Pre-steering would enable disparate frequencies over a wide band to be coherently summed, to provide coherent gain in the look direction (over the band) by providing additional sample support for the sample covariance estimation.}
